Dark Control:\\ A Unified Account of Default Mode Function\\ by Control Theory and Reinforcement Learning

### 2017-04-17 paper/paper.tex
supra-pass part 3

\subsection{Towards a formal account of DMN function}
We argue that DMN implication in a
diversity of humans' most advanced cognitive processes
can be parsimoniously recast as prediction error minimization
based on pervasive probabilistic simulations,
thus maximizing action outcome across multiple time scales.
Such a purposeful optimization objective
may be solved by a stochastic approximation
based on a brain implementation of Markov Chain Monte Carlo (MCMC) sampling
\citep{tenenbaum2011grow}.
In this context,
\textit{control} refers to the influence that an agent exerts when interacting
with the environment to encourage preferred states.
Even (necessarily imperfect) memory retrieval,
random day-time mind-wandering, and dreams during sleep
may provide meaningful building blocks to iteratively improve
the predictive DMN machinery to optimize the behavior of the organism.
%
It has indeed been proposed earlier that
the human brain's energy budget is largely dedicated to
``the development and maintenance of [a]
probabilistic model of anticipated events''
\citep{raichle2005intrinsic}.
This idea has been invigorated by
empirical evidence from
neuroscientific experiments \citep{kording2004bayesian, fiser2004small}.
The present paper proposes a
process model that satisfies this contention.

@@

The retrosplenial portion of the PMC can subserve
representation of action possibilities
and evaluation of reward contingencies by integration with
information from memory and different perspective frames.
Regarding memory retrieval, retrosplenial lesions have been
consistently associated with anterograde and retrograde memory impairments
of various kinds of sensory information
in rabbits and humans
\citep{vann2009does}.
Regarding perspective frames, the retrosplenial subregion of the PMC has been
proposed to mediate between the organism's egocentric
(i.e., focused on sensory input) and
allocentric (i.e., focused on world knowledge) viewpoints
in animals and humans
\citep{epstein2008parahippocampal, burgess2008spatial, valiquette2007different}.

@@

Generally,
patients with neurological lesions in the prefrontal cortex
are known to struggle with
adaption to novel situations and stimuli
\citep{stuss1986frontal}.
The dmPFC may subserve inference, representation, and assessment
of one's own and other individuals' action considerations.
Specifically, neural activity in the human dmPFC
reflected expectations about other peoples' actions and
errors in these predictions.
Neural activity in the dmPFC indeed explained the proficiency decline
of inferring other peoples' thoughts in aging humans \citep{moran2012social}.
Some dmPFC neurons in macaque monkeys exhibited a preference
for processing others', rather than own, behavior
with fine-grained adjustment of contextual circumstances \citep{yoshida2010neural}.
In fact, the topographically neighboring dorsal anterior cingulate cortex
has also been linked to computing values and efforts of
persisting a behavioral plan versus switching the
environmental context in several lesion studies \citep{kolling2016value}.
%
Such highly abstract neural computations necessarily rely on the
generation of probabilistic internal information drawing from
episodic memory retrieval, generative construction processes,
and explicit knowledge of the external world.
%
In a computational neuroimaging experiment,
dorsomedial PFC activity preferentially modeled the consequences of
action choices that were not actually executed,
whereas ventromedial PFC (vmPFC) activity
modeled especially value outcomes of performed actions in the environment
\citep{nicolle2012agent}.

@@

While the HC
is traditionally believed to allow remembering the past,
there is now increasing evidence for a role
in constructing mental models in general
\citep{maguire2016, schacter2007remembering, gelbard2008internally, Javadi2017}.
Its recursive anatomical architecture
may be specifically designed to allow reconstructing
entire episodes of experience from memory fragments.
Indeed,
hippocampal damage is
not only associated with an impairment in reexperiencing the past (i.e., amnesia),
but also imagining about one's own future and
 new fictitious experiences more broadly \citep{hassabis2007patients}.
Mental scenes created by HC-lesioned patients exposed a lack of
spatial integrity, richness in detail, and overall coherence.
%
Single-cell recordings in the animal HC revealed
some constantly active neuronal ensembles whose firing coincided with
distinct locations in space during environmental navigation.
London taxi drivers, individuals with high performance in spatial navigation,
were shown to exhibit increased gray-matter volume in the
HC \citep{maguire2000navigation}.
Indeed, when an animal is choosing between alternative
paths, the corresponding neuronal populations in the HC
spike one after another  \citep{johnson2007neural}.
These neuronal patterns appear to also indicate upcoming behavior
\citep{pfeiffer2013hippocampal}.

But encoding and generative reconstruction in the HC extends
beyond mere spatial knowledge of the environment.
Based on large-scale recordings of hippocampal neuronal populations,
complex spiking patterns can be followed across extended periods including
their modification of input-free self-generated patterns
after environmental events \citep{buzsaki2004large}.
Specific spiking sequences, that were elicited in experimental task conditions,
have been shown to be reenacted spontaneously during
quiet wakefulness and sleep \citep{hartley2014space, o2010play}.
Moreover, spike sequences measured in hippocampal place cells of rats
featured re-occurrence directly after experimental trials
as well as directly before upcoming experimental trials \citep{diba2007forward}.
Such hippocampal ensembles burt during rest and sleep
have been proposed to be critical in communicating local information
to the neocortex for long-term storage, potentially also in the nodes of the DMN.
These HC-subserved mechanisms
probably contribute to
recollecting autobiographical memory episodes, as well as
reexperiencing or newly generating mental scenarios
\citep{hassabis2007patients}.

The HC thus orchestrates experience of environmental aspects for
consolidations based on reenactment and for integration into
rich mental scene construction \citep{deuker2016event, bird2010establishing}.
In this way, the HC may influence
ongoing perception in the current environment
\citep{maguire2016}.
% (TODO: relate to self-play in deepmind Go).
% (TODO: Kai had an interesting idea: the deja-vu effect
% could be when you already accidentally perturbed past
% such that it really occures in reality later.)

\subsection{The right and left TPJ: prediction error signaling and world semantics}
The DMN emerges with its midline structures early in human development.
However,
the right and left TPJ may become fully integrated into this canonical
network only after birth \citep{doria2010}.
The TPJs are known to exhibit hemispheric differences
based on cytoarchitectonic borders and gyrification pattern
\citep{seghier2013angular}.
Neuroscientific investigations on hemispheric functional specialization
have highlighted the right versus left cerebral hemisphere as dominant for
attention versus language functions.

The TPJ in the right hemipshere (RTPJ) is central for
action initiation during externally structured tasks and
sensorimotor control by integrating supra-modal stimulus-guided attention
\citep{corbetta2002control}.
Involvement of this DMN node was repeatedly reported in
multi-step action execution \citep{hartmann2005takes},
visuo-proprioceptive conflict \citep{Balslev2005} and
multi-modal detection of sensory changes across
visual, auditory, or tactile stimulation in a multi-modal fMRI study
\citep{downar2000multimodal}.
In humans, direct electrical stimulation of the
RTPJ during neurosurgery was associated with altered perception
and stimulus awareness \citep{blanke2002neuropsychology}.
%
Importantly, the RTPJ has been shown to be intimately related to
supra-modal prediction and error signaling.
It was argued that the RTPJ encodes actions and ensuing outcomes
without necessarily relating those to outcome value
\citep{liljeholm2013neural, hamilton2008action,
jakobs2009effects}.
Neural activity in the RTPJ has been argued to be responsible
for stimulus-driven attentional reallocation to
salient and surprising sources of information
as a ‘‘circuit breaker’’ that recalibrates control and maintenance systems
\citep{bzdok2013tpj, corbettashul2008}.
% (Bzdok et al., 2013; Corbetta et al., 2008).
Indeed, patients with RTPJ damage have particular difficulties
with multistep actions \citep{hartmann2005takes}.
In the face of large discrepancies between actual and previously predicted
environmental events the RTPJ acts a potential switch between
externally-oriented mind sets focussed on the
sensory world and internally-oriented mind sets focussed
on self-relevant mental scene construction.
Transient RTPJ lesion in humans for instance diminished the
impact of predicted intentions of other individuals
\citep{young2010disruption},
a capacity believed to be subserved by the DMN.
The RTPJ might hence be an important relay that shifts away
from the ‘‘internally directed’’ baseline processes
to, instead, deal with (unexpected) environmental objects and events.
% (TODO: slow endogeneous changes in state transitions by the policy and value matrices)

The TPJ in the left hemisphere (LTPJ), in turn, exhibits a close topographical relationship to Wernicke's area
involved in understanding spoken and written language.
Neurological patients with damage caused to Wernicke's area
have a major impairment of language comprehension
when listening to others or reading a book.
Their speech
preserves natural rhythm and about normal syntax, yet the
voiced sentences are devoid of meaning (i.e., aphasia).
Abstracting from the typical semantic interpretations in linguistics
and neuropsychology,
the LTPJ probably mediates access to and integration of world knowlege
to model action concepts
\citep{binder2011neurobiology, seghier2013angular}.
For instance, LTPJ lesions also entail problems in recognizing
others' pantomimed action towards objects
without obvious relation to processing explicit language content
\citep{varney1987locus}.
% (Varney and Damasio 1987; Rothi et al. 1991; Buxbaum et al. 2005).
%
Inner speech also hinges on knowledge retrieval
about the physical and inter-personal world.
Indeed,
the internal production of
verbalized thought ("language of the mind") was closely related to the left TPJ
in a multivariate analysis of brain volume
\citep{geva2011neural}.
Further,
episodic memory recall and imagination strongly draw on
reassembling world knowledge.
Isolated building blocks of world statistics probably get reassembled
in internally generated visual scenarios that
navigate present action, weigh hypothetical possibilities, and forecast the future.
%
The LTPJ may hence facilitate the automated prediction of events
by incorporating experience-derived representations of the world
into ongoing action, planning, and problem solving.
% world -> policy matrix driven computation
% self -> value matrix driven computation

@@

In comparison,
both the semantic hypothesis and MDPs expose mechanisms of
how action considerations could be mentally explored.
In both accounts,
there is also no evidence to indicate that predictions of various
levels of complexity, abstraction, timescale and purpose
use mechanisms that are qualitatively different. This concurs with
DMN activity increases across time, space, and content domains
demonstrated in many neuroimaging studies \citep{spreng2009common}.
The semantic hypothesis
and MDP account provide explanations why hippocampus lesion does
not only impair retrieving memories, but also hypothetical and future
thinking \citep{hassabis2007patients}.
While both semantic hypothesis and
our formal account propose memory-based internally
generated information for probabilistic mental models of action outcomes,
MDPs render explicit the grounds on which the final action is
eventually chosen, namely, the estimated cumulative reward.
\textbf{The notion of semantic knowledge associations is
incorporated into the MDP as the Markov property,
that is, the current state directly results from the
agent's history of states and actions. The learned
value estimations and action transition schedules drive
stimulus processing and action choice in the present.}
The MDPs naturally integrate the former egocentric
(more related to current action, state and reward) and the later
allocentric (more related to past and future actions, states, and rewards)
angles on the world in a same optimization problem.
Further,
the semantic account of DMN function does not offer
a mechanistic explanation how explicit world knowledge and semantic analogies thereof
lead to prediction of future actions and states.
The semantic hypothesis does not explain why memory recall
for scene construction in humans is typically fragmentary and noisy
instead of accurate and reliable.
In contrast to existing accounts on semantics and
mental scene construction, the random and creative aspects of DMN function
are explained in MDPs by the advantages of stochastic optimization.
Yet, the MDP framework provides an algorithmic explanation in that
stochasticity of the parameter space explored
by the Monte Carlo solvers achieves better fine-tuning of the
action policies and estimation of expected reward outcomes.
That is, the purposeful stochasticity of policy and value estimation
in MDPs provides a candidate explanation for why humans
have evolved imperfect noisy memories
as the more advantageous adaptation.
In sum, episodic scene construction according to the semantic
account is lacking an explicit time and incentive model.

@@

\section{Conclusion}
What brain function could be important enough
for the existence and survival of the human species
to warrant constant, high energy costs?
MDPs provide an attractive
process model how the human association cortex
might implement supra-modal representation and control of the environment to
optimize the organism's fate.
% by obtaining reward and avoiding pain.
This idealized process model explains
a number of previous experimental observations in the
DMN by a simple but non-trivial mechanism.
%
From the computational view of a Markovian sequential decision process,
behavior unfolds by integrating happened past events
and possible future events to guide action choice in the present context.
This functional account is more compatible with the DMN's
poorly understood involvement across
autobiographical memory retrieval, problem solving,
abstract reasoning based on internally generated scenes, social cognition,
as well as delay discounting and self-related prospection.
MDPs provide a mathematical formalism how
optimal substructure in the environment can be recursively exploited
when confronted with complicated decisions.
Improvement of the internal world model
by injecting stochasticity in the recall of past
actions and outcomes may explain why
very accurate memories have been disfavored in human evolution
and why human creativity might be adaptive.
%
In principle,
neuroscientific experiments can be designed that operationalize
the set of action, value, and state variables that determine
the behavior of intelligent RL systems.
The proposed machine-learning perspective
on DMN biology is hence not only practically computable but
also yields falsifiable neuroscientific hypotheses.
At the least, we propose an alternative vocabulary to
describe and interpret experimental findings in neuroscience studies
on the DMN.
%
Ultimately,
the DMN can be viewed as a functional integrator
from the relatively recent events to anticipated upcoming events
in order to constantly improve action in our dynamic world.

>>>>

\subsection{Towards a formal account of DMN function}
We argue that DMN implication in a
diversity of humans' most advanced cognitive processes
can be parsimoniously recast as prediction error minimization
based on pervasive probabilistic simulations,
thus maximizing action outcome across multiple time scales.
Such a purposeful optimization objective
may be solved by a stochastic approximation
based on a brain implementation of Markov Chain Monte Carlo (MCMC) sampling
\citep{tenenbaum2011grow}.
In this context,
\textit{control} refers to the influence that an agent exerts when interacting
with the environment to encourage preferred states.
Even (necessarily imperfect) memory recall,
random day-time mind-wandering, and dreams during sleep
may provide meaningful building blocks to iteratively improve
the predictive DMN machinery to optimize the behavior of the organism.
%
It has indeed been proposed earlier that
the human brain's energy budget is largely dedicated to
``the development and maintenance of [a]
probabilistic model of anticipated events''
\citep{raichle2005intrinsic}.
This idea has been invigorated by
empirical evidence from
neuroscientific experiments \citep{kording2004bayesian, fiser2004small}.
The present paper proposes a
process model that satisfies this contention.

@@

The retrosplenial portion of the PMC can subserve
representation of action possibilities
and evaluation of reward contingencies by integration with
information from memory and different perspective frames.
Regarding memory recall, retrosplenial lesions have been
consistently associated with anterograde and retrograde memory impairments
of various kinds of sensory information
in rabbits and humans
\citep{vann2009does}.
Regarding perspective frames, the retrosplenial subregion of the PMC has been
proposed to mediate between the organism's egocentric
(i.e., focused on sensory input) and
allocentric (i.e., focused on world knowledge) viewpoints
in animals and humans
\citep{epstein2008parahippocampal, burgess2008spatial, valiquette2007different}.

@@

Generally,
patients with neurological lesions in the prefrontal cortex
are known to struggle with
adaption to novel situations and stimuli
\citep{stuss1986frontal}.
The dmPFC may subserve inference, representation, and assessment
of one's own and other individuals' action considerations.
Specifically, neural activity in the human dmPFC
reflected expectations about other peoples' actions and
errors in these predictions.
Neural activity in the dmPFC indeed explained the proficiency decline
of inferring other peoples' thoughts in aging humans \citep{moran2012social}.
Some dmPFC neurons in macaque monkeys exhibited a preference
for processing others', rather than own, behavior
with fine-grained adjustment of contextual circumstances \citep{yoshida2010neural}.
In fact, the topographically neighboring dorsal anterior cingulate cortex
has also been linked to computing values and efforts of
persisting a behavioral plan versus switching the
environmental context in several lesion studies \citep{kolling2016value}.
%
Such highly abstract neural computations necessarily rely on the
generation of probabilistic internal information drawing from
episodic memory recall, generative construction processes,
and explicit knowledge of the external world.
%
In a computational neuroimaging experiment,
dorsomedial PFC activity preferentially modeled the consequences of
action choices that were not actually executed,
whereas ventromedial PFC (vmPFC) activity
modeled especially value outcomes of performed actions in the environment
\citep{nicolle2012agent}.

@@

While the HC
is traditionally believed to allow remembering the past,
there is now increasing evidence for a role
in constructing mental models in general
\citep{maguire2016, schacter2007remembering, gelbard2008internally, Javadi2017}.
Its recursive anatomical architecture
may be specifically designed to allow reconstructing
entire episodes of experience from memory fragments.
Indeed,
hippocampal damage is
not only associated with an impairment in reexperiencing the past (i.e., amnesia),
but also imagining one's own future and
fictitious experiences more broadly \citep{hassabis2007patients}.
Mental scenes created by HC-lesioned patients exposed a lack of
spatial integrity, richness in detail, and overall coherence.
%
Single-cell recordings in the animal HC revealed
some constantly active neuronal ensembles whose firing coincided with
specific locations in space during environmental navigation.
London taxi drivers, individuals with high performance in spatial navigation,
were shown to exhibit increased gray-matter volume in the
HC \citep{maguire2000navigation}.
Indeed, when an animal is choosing between alternative
paths, the corresponding neuronal populations in the HC
spike one after another  \citep{johnson2007neural}.
These neuronal patterns appear to also indicate upcoming behavior
\citep{pfeiffer2013hippocampal}.

HC function probably extend beyond simple forms of
encoding and reconstruction of memory and spatial information.
Based on large-scale recordings of hippocampal neuronal populations,
complex spiking patterns can be followed across extended periods including
their modification of input-free self-generated patterns
after environmental events \citep{buzsaki2004large}.
Specific spiking sequences, which were elicited in experimental task conditions,
have been shown to be reenacted spontaneously during
quiet wakefulness and sleep \citep{hartley2014space, o2010play}.
Moreover, spike sequences measured in hippocampal place cells of rats
featured re-occurrence directly after experimental trials
as well as directly before upcoming experimental trials \citep{diba2007forward}.
Such hippocampal ensembles burt during rest and sleep
have been proposed to be critical in communicating local information
to the neocortex for long-term storage, potentially also in the nodes of the DMN.
These HC-subserved mechanisms
probably contribute to advanced cognitive processes that require
recollecting autobiographical memory episodes, as well as
reexperiencing or newly generating mental scenarios
\citep{hassabis2007patients}.

The HC thus orchestrates experience of environmental aspects for
consolidations based on reenactment and for integration into
rich mental scene construction \citep{deuker2016event, bird2010establishing}.
In this way, the HC may contribute to improving
ongoing perception of and action on the environment
\citep{maguire2016}.
% (TODO: relate to self-play in deepmind Go).
% (TODO: Kai had an interesting idea: the deja-vu effect
% could be when you already accidentally perturbed past
% such that it really occures in reality later.)

\subsection{The right and left TPJ: prediction error signaling and world semantics}
The DMN emerges with its midline structures early in human development
\citep{doria2010}.
However,
the right and left TPJ may become fully integrated into this canonical
network only after birth.
The TPJs are known to exhibit hemispheric differences
based on cytoarchitectonic borders and gyrification pattern
\citep{seghier2013angular}.
Neuroscientific investigations on hemispheric functional specialization
have highlighted the right versus left cerebral hemisphere as dominant for
attention versus language functions.

The TPJ in the right hemipshere (RTPJ) 
has been shown to be intimately related to
supra-modal prediction and error signaling.
It is probably central for
action initiation during externally structured tasks and
sensorimotor control by integrating supra-modal stimulus-guided attention
\citep{corbetta2002control}.
Involvement of this DMN node was repeatedly reported in
multi-step action execution \citep{hartmann2005takes},
visuo-proprioceptive conflict \citep{Balslev2005}, and
multi-modal detection of sensory changes across
visual, auditory, or tactile stimulation in a multi-modal fMRI study
\citep{downar2000multimodal}.
In humans, direct electrical stimulation of the
RTPJ during neurosurgery was associated with altered perception
and stimulus awareness \citep{blanke2002neuropsychology}.
%
It was argued that the RTPJ encodes actions and ensuing outcomes
without necessarily relating those to outcome value
\citep{liljeholm2013neural, hamilton2008action,
jakobs2009effects}.
Neural activity in the RTPJ has been argued to be responsible
for stimulus-driven attentional reallocation to
salient and surprising sources of information
as a ‘‘circuit breaker’’ that recalibrates control and maintenance systems
\citep{bzdok2013tpj, corbettashul2008}.
% (Bzdok et al., 2013; Corbetta et al., 2008).
Indeed, patients with RTPJ damage have particular difficulties
with multistep actions \citep{hartmann2005takes}.
In the face of large discrepancies between actual and previously predicted
environmental events the RTPJ acts as a potential switch between
externally-oriented mind sets focussed on the
sensory world and internally-oriented mind sets focussed
on self-relevant mental scene construction.
Transient RTPJ lesion in humans for instance diminished the
impact of predicted intentions of other individuals
\citep{young2010disruption},
a capacity believed to be enabled by the DMN.
The RTPJ might hence be an important relay that shifts away
from the ‘‘internally directed’’ baseline processes
to, instead, deal with (unexpected) environmental objects and events.
% (TODO: slow endogeneous changes in state transitions by the policy and value matrices)

The TPJ in the left hemisphere (LTPJ), in turn, exhibits a close topographical relationship to Wernicke's area
involved in understanding spoken and written language.
Neurological patients with damage caused to Wernicke's area
have a major impairment of language comprehension
when listening to others or reading a book.
Their speech
preserves natural rhythm and about normal syntax, yet the
voiced sentences are devoid of meaning (i.e., aphasia).
Abstracting from the typical semantic interpretations in linguistics
and neuropsychology,
the LTPJ probably mediates access to and integration of world knowlege,
such as required during action considerations
\citep{binder2011neurobiology, seghier2013angular}.
For instance, LTPJ lesions also entail problems in recognizing
others' pantomimed action towards objects
without obvious relation to processing explicit language content
\citep{varney1987locus}.
% (Varney and Damasio 1987; Rothi et al. 1991; Buxbaum et al. 2005).
%
Inner speech also hinges on knowledge recall
about the physical and inter-personal world.
Indeed,
the internal production of
verbalized thought ("language of the mind") was closely related to the LTPJ
in a multivariate analysis of brain volume
\citep{geva2011neural}.
Further,
episodic memory recall and imagination strongly draw on
reassembling world knowledge.
Isolated building blocks of world statistics probably get reassembled
in internally generated visual scenarios that
navigate present action, weigh hypothetical possibilities, and forecast the future.
%
The LTPJ may hence facilitate the automated prediction of events
by incorporating experience-derived representations of the world
into ongoing action, planning, and problem solving.
% world -> policy matrix driven computation
% self -> value matrix driven computation

@@

In comparison,
both the semantic hypothesis and MDPs expose mechanisms of
how action considerations could be mentally explored.
In both accounts,
there is also no evidence to indicate that predictions of various
levels of complexity, abstraction, timescale and purpose
use mechanisms that are qualitatively different. This concurs with
DMN activity increases across time, space, and content domains
demonstrated in many neuroimaging studies \citep{spreng2009common}.
The semantic hypothesis
and MDP account provide explanations why hippocampus lesion does
not only impair recalling memories, but also hypothetical and future
thinking \citep{hassabis2007patients}.
While both semantic hypothesis and
our formal account propose memory-based internally
generated information for probabilistic mental models of action outcomes,
MDPs render explicit the grounds on which the final action is
eventually chosen, namely, the estimated cumulative reward.
\textbf{The notion of semantic knowledge associations is
incorporated into the MDP as the Markov property,
that is, the current state directly results from the
agent's history of states and actions. The learned
value estimations and action transition schedules drive
stimulus processing and action choice in the present.}
The MDPs naturally integrate the former egocentric
(more related to current action, state and reward) and the later
allocentric (more related to past and future actions, states, and rewards)
angles on the world in a same optimization problem.
Further,
the semantic account of DMN function does not offer
a mechanistic explanation how explicit world knowledge and semantic analogies thereof
lead to prediction of future actions and states.
The semantic hypothesis does not explain why memory recall
for scene construction in humans is typically fragmentary and noisy
instead of accurate and reliable.
In contrast to existing accounts on semantics and
mental scene construction, the random and creative aspects of DMN function
are explained in MDPs by the advantages of stochastic optimization.
Yet, the MDP framework provides an algorithmic explanation in that
stochasticity of the parameter space explored
by the Monte Carlo solvers achieves better fine-tuning of the
action policies and estimation of expected reward outcomes.
That is, the purposeful stochasticity of policy and value estimation
in MDPs provides a candidate explanation for why humans
have evolved imperfect noisy memories
as the more advantageous adaptation.
In sum, episodic scene construction according to the semantic
account is lacking an explicit time and incentive model.

@@

\section{Conclusion}
What brain function could be important enough
for the existence and survival of the human species
to warrant constant, high energy costs?
MDPs provide an attractive
process model how the human association cortex
might implement supra-modal representation and control of the environment to
optimize the organism's fate.
% by obtaining reward and avoiding pain.
This idealized process model explains
a number of previous experimental observations in the
DMN by a simple but non-trivial mechanism.
%
From the computational view of a Markovian sequential decision process,
behavior unfolds by integrating happened past events
and possible future events to guide action choice in the present context.
This functional account is more compatible with the DMN's
poorly understood involvement across
autobiographical memory recall, problem solving,
abstract reasoning based on internally generated scenes, social cognition,
as well as delay discounting and self-related prospection.
MDPs provide a mathematical formalism how
optimal substructure in the environment can be recursively exploited
when confronted with complicated decisions.
Improvement of the internal world model
by injecting stochasticity in the recall of past
actions and outcomes may explain why
very accurate memories have been disfavored in human evolution
and why human creativity might be adaptive.
%
In principle,
neuroscientific experiments can be designed that operationalize
the set of action, value, and state variables that determine
the behavior of intelligent RL systems.
The proposed machine-learning perspective
on DMN biology is hence not only practically computable but
also yields falsifiable neuroscientific hypotheses.
At the least, we propose an alternative vocabulary to
describe and interpret experimental findings in neuroscience studies
on the DMN.
%
Ultimately,
the DMN can be viewed as a functional integrator
from the relatively recent events to anticipated upcoming events
in order to constantly improve action in our dynamic world.
